Optimal (Multiway) Spatial Joins

### 2024-05-28 msj.tex
yufei

\def\vgap{\vspace{0mm}}
\def\extraspacing{\vspace{2mm} \noindent}
\def\figcapup{\vspace{-2mm}}
\def\figcapdown{\vspace{-4mm}}

@@

In the {\em triangle detection}, we are given an undirected graph $G = (V, E)$ and need to determine whether $G$ has a triangle (a.k.a.\, 3-clique). Set $m = |E|$. We consider that $G$ has no isolated vertices (namely, vertices with degree 0), and therefore $|V| \le 2m$.

>>>>

\def\vgap{\vspace{0mm}}
\def\extraspacing{\vspace{1.5mm} \noindent}
\def\figcapup{\vspace{-2mm}}
\def\figcapdown{\vspace{-2mm}}

@@

In the {\em triangle detection} problem, we are given an undirected graph $G = (V, E)$ and need to determine whether $G$ has a triangle (a.k.a.\, 3-clique). Set $m = |E|$. We consider that $G$ has no isolated vertices (namely, vertices with degree 0), and therefore $|V| \le 2m$.
